\section{Three Desiderata for Abstraction in RL}

We propose the following three desiderata on abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
\begin{enumerate}
\item \textsc{Compressibility}: An abstraction ought to compress $M_G$ to be significantly smaller. \footnote{where smallness is understood as in \cite{littman1995complexity}, with respect to $|\mathcal{S}|$, $|\mathcal{A}|$, and the information content required to represent input-output pairs of $\mathcal{T}$ and $\mathcal{R}$.}
\item \textsc{Optimality}: An abstraction ought to induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
\item \textsc{Efficient-Computability}: An abstraction ought to consist of information that is easier to compute than $\pi^*$ for $M_G$.
\end{enumerate}

% Defense of the desiderata.
Abstraction, more generally, is aimed at reducing the dimensionality of an entity; this {\it reduction} is captured by \textsc{Compressibility}, while the {\it preservation} of critical information content of the entity is captured by \textsc{Optimality}. The third criteria is relevant to planning and RL; that the information relevant to the abstraction be easy to compute. We take these three statements as guiding principles on abstractions for planning and \ac{RL}. \dnote{Note about how to satisfy them? What does it look like for one to be satisfied?}

All three desiderata are trivial to satisfy on their own. Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action). Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP. Now consider \textsc{Optimality}. Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$. The optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}. Lastly for \textsc{Efficient-Computability}, returning an MDP $M_A$, such that $M_A$ is identical to $M_G$ is trivially efficiently computable.

The case of interest is an abstraction that satisfies {\it all three} desiderata.\footnote{Note that satisfying any {\it two} criteria is also trivial} To the best of our knowledge, no existing abstraction has been formally proven to satisfy all three desiderata (or something similar to all three).

In the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.