\section{Relevance to Our Recent Work}

% Paragraph on approximate state abstraction
% We propose epsilon extension of Lihong.
In this document, we offered three desiderata on abstractions in RL. We take these as guiding principles for methods of abstraction.

In search of abstractions that satisfy all three desiderata, including \textsc{Efficient-Computability}, our recent work on approximate state abstraction~\cite{abelhershko2016approx} developed an $\epsilon$-relaxation of the conditions proposed in \cite{li2006towards}.
We consider the abstraction pipeline in which, given a ground MDP $M_G$, an approximate state abstraction function induces a full abstract \ac{MDP} $M_A$. We then apply the optimal abstract policy, $\pi_{GA}$, in the ground MDP; our main result bounds the sub-optimality of this policy for four types of approximate abstraction functions:
\begin{thm}
There exist at least four classes of approximate state abstraction\footnote{Analogously interpreted as state-aggregation functions.} functions for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\varepsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\varepsilon \right).
\end{equation}
\end{thm}

This theorem suggests that approximate state abstractions satisfy the \textsc{Value} desiderata. Moreover, we suspect that functions of these types are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}. Furthermore, in this work we empirically demonstrate the compressibility of these functions, and consider it an open problem of analysis as to what degree of compressibility is achievable under this framework.

We can formally ground each desiderata in the language of this framework as follows:
\begin{enumerate}
%Compressibility
\item \textsc{Compressibility}: $|\mcS_G - \mcS_A| \geq B_1$ and $|\mcA_G - \mcA_A| \geq B_2$ where $B_1$ and $B_2$ are ``sufficiently" large.

%Optimality
\item \textsc{Optimality}: $\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}} \leq B_3$ where $B_3$ is not ``unreasonably" large.

%Efficient-Computability
\item \textsc{Efficient-Computability}: $\widetilde{\phi}_f$ and $\Delta_g$ ought to be polynomially computable in the relevant quantities, namely $\mcS_G$, $\mcA_G$ and the representation of $\mcT$ and $\mcR$.
\end{enumerate}

Such a formal treatment will enable extension to questions regarding the utility of temporal abstractions.

To incorporate temporally extended actions, we consider pair of functions: $(\widetilde{\phi}_f, \Delta_g)$, where:
\begin{equation}
\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g : \mathcal{A}_G \mapsto \mathcal{A}_A
\end{equation}

Now, the abstract MDP is fully distinct from $M_G$, in that it also has a unique set of abstract actions. As before, we can prove bounds on the value lost under different {\it kinds} of functions $\Delta_g$, which will provide a clear distinction between which abstract actions can preserve value, and which do not. In future work, we are interested in characterizing precisely what types of abstract actions can satisfy these desiderata, using this framework.


% DISCUSSION?


